% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author)
%       http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com>
%       http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com>
%       http://www.courtesan.com/todd
% (c) 2009-2010 George R. Louthan IV <georgerlouth@nthefourth.com>
%       http://georgerloutha.nthefourth.com
%
% This work is licensed under the Creative Commons Attribution-Noncommercial-
% Share Alike 2.5 License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to:
%

\documentclass[letterpaper,11pt]{article}
\usepackage[pagesetup]{tucv}

% For PDF metadata:
\title{George R Louthan - Resume}
\author{George R Louthan IV}

\begin{document}

% Heading and name/contact info table
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large George R. Louthan IV}  & 918.289.2458\\
20 E. Archer \#604 &  georgerlouth@nthefourth.com \\
Tulsa, OK 74103 & http://georgerloutha.nthefourth.com \\
\end{tabular*}

\resheading{Objective}
\begin{itemize}
\item[] \resentrysinglecol{I want to do computer stuff.}
\item[] \resentrysinglecol{Available June 2011.}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item[]
    \resschool{University of Tulsa}{Tulsa, OK}
        \resdegree[Thesis related to formal methods and cyber-physical systems]
            {Master of Science}{Computer Science}{May 2011 \newline (expected)}
        \resdegree{Bachelor of Science}{Computer Science}{May 2009}
        \resdegree{Bachelor of Science}{Mathematics}{May 2009}
\end{itemize}
\resheading{Certifications}
\begin{itemize}
\item[]
    \resschool[National Information Assurance Training Standards]
        {Committee on National Security Systems 4011--4016}{Tulsa, OK}
        \ressubentry{4011 Information Systems Security Professional}{May 2006}
        \ressubentry{4012 Senior Systems Manager}{Dec 2007}
        \ressubentry{4013 System Administrator}{May 2010}
        \ressubentry{4014 Information Systems Security Officer}{May 2011}
        \ressubentry{4015 System Certifier}{Dec 2009}
        \ressubentry{4016 Risk Analyst}{May 2010}
\end{itemize}

\resheading{Academics}
    \begin{itemize}
    \item[] \resdesc{Instructor}{Information Security: Assurance and Risk Assessment
        (short course---taught applied portions), Fundamentals of Algorithms
        and Computer Applications Lab}
    \item[] \resdesc{Teaching Assistant}{Fundamentals of Algorithms and Computer
        Applications Lecture}
    \item[] \resdesc{Referee}{Journal of Supercomputing (Jan 2010)}
    \item[] \resdesc{Information Assurance Coursework}{Network Security, Secure
        System Administration, Risk Management for Information Systems,
        Information Systems Assurance, Enterprise Security Management,
        Computer Security, Computer Forensics, Applied Cyber Defense
        (independent study)}
    \item[] \resdesc{Computer Science Coursework}{Mobile Device Application Development,
        Computational Neuroscience, Machine
        Learning, Senior Software Projects, Compiler Construction, Operating
        Systems, Artificial Intelligence, Computer Animation, Computer Networks,
        Computer Network Analysis (independent study)}
    \item[] \resdesc{Mathematics Coursework}{Numerical Methods, Numerical Methods for
        IVP/BVP PDEs, Modern Algebra, Real Analysis, Linear Algebra, Mathematics
        Seminar (a survey of unusual problems)}
\end{itemize}
\newpage
\resheading{Skill Set}
\begin{itemize}
\item[] \resdesc{Languages}{Python; Java; Lisp (Clojure and Common Lisp);
    \LaTeX; Mathematica; some Ruby, Perl, PHP, and Objective C}
\item[] \resdesc{Platforms}{Linux (especially Debian/Ubuntu, also 
	OpenWRT/FreeWRT);
	Windows (modern workstation and server versions);
	VMWare ESXi (3 and 4); Mac OS X}
\item[] \resdesc{Technologies}{Computer networking (TCP/IP); Virtualization;
	Firewalls (iptables and Shorewall,
	some pf and Cisco); Django; Version control (Subversion and Mercurial);
	Network monitoring and IDS; Android OS; iOS; Application
	security; Forensics; PKI}
\item[] \resdesc{Processes}{Risk management for information systems (NIST SP 
	800-30),
	including some familiarity with IT aspects of Sarbanes-Oxley risk assessment
	(PCAOB Auditing Standard 5); Information Security Management 
	(ISO/IEC 17799:2005);
	Information Assurance Controls and Accreditation 
	(NIST SP 800-53 and DoDI 8510.01);
	Incident response and computer forensics; General policy development;
	General familiarity with NIST 800 series}
\item[] \resdesc{Mathematics}{Numerical analysis; Finite difference methods;
	Finite element analysis;
	Real analysis; Discrete mathematics; Modern algebra; Finite state automata;
	Hybrid automata; Process calculi; Analysis of algorithms}
\item[] \resdesc{Soft skills}{Very strong written 
	and verbal communication skills;
	Skilled at explaining technical concepts to laypeople;
	Comfortable in social settings; Experienced and extremely comfortable giving
	lectures and presentations}
\end{itemize}

\resheading{Employment History}
\begin{itemize}
\item[]
\resemployer[Research university with a prestigious information security program
        and extensive research operations under its Institute for Information
        Security, an NSA/CSS Center of Excellence in information assurance.]
        {University of Tulsa}{Tulsa, OK}
    \resjob[Information security engineering student lead for formal methods
        research. Collaborating with researchers in cyber security
        training, information visualization, and critical infrastructure
        protection initiatives. Peer-reviewed publications in cyber security
        education, network intelligence, and secure collaboration.
        Led the development and deployment of the Institute's IT infrastructure
        and supervising its upkeep (approximately 40 workstations and 5 servers).]
        {Graduate Research Assistant}{May 2009}{Present}
    \resjob[Taught a sophomore-level programming lab in the Java language. Developed
        supplementary course materials on code style, algorithms, documentation,
        and best practices.]{Graduate Teaching Assistant}{Jan 2010}{May 2010}
    \resjob[Undergraduate researcher in the Enterprise Security Group. Worked in
        enterprise security management, threat modeling, network intelligence,
        and information visualization. Peer-reviewed publications in network
        intelligence.]{Undergraduate Research Scientist}{May 2006}{May 2009}
\item[]
\resemployer[Custom software contractor, working in database and web
        services.]{IV Consulting, Inc.}{Tulsa, OK}
    \resjob[Co-founder of the company as well as web and database developer in
        Python's Django framework. Developing two production systems for patient
        management and subject tracking for a psychiatric hospital and brain
        research institution. Responsible for back-end web development,
        project management, client relations, and documentation.]
        {Co-owner/Developer}{Jul 2010}{Present}
\item[]
\resemployer[Technology start-up company that produced a web-based multi-factor
        authentication product and advertising platform.]{Vidoop}{Tulsa, OK}
    \resjob[Performed a vulnerability assessment on the user-facing portions of
        the company's authentication product. Developed proof-of-concept code
        for several attacks, including bypassing the product's CAPTCHA
        properties using computer vision. Delivered a comprehensive report and
        developed proof-of-concept mitigation strategies.]
        {Security Research Intern}{May 2008}{Sep 2008}
    \resjob[Served as a copy writer and editor for technical documentation,
        specifications, white papers, user documentation, and marketing
        materials. Developed and narrated a series of educational videos for
        Vidoop's products and OpenID. Primary author on the corporate blog.
        Worked closely with developers and business personnel. Staffed exhibit
        at IT Security World.]{Technical Writing Intern}{May 2007}{Mar 2009}
\end{itemize}


\resheading{Projects}

\begin{itemize}
\item[]
\resemployer[Project for the wireless collection and remote analysis of
        patients' weights as automatically recorded by a cellular-enabled scale.
        Collaboration with Alexander Barclay (Laureate Institute for Brain
        Research) and Kevin Hall (National Institute of Diabetes and Digestive
        and Kidney Diseases).]{GSM Scale}{Tulsa, OK}
    \resjob[Designing and developing the scale client hardware and software, as
        well as participating in the specification of reporting protocols and
        web service API.]{Bench-to-Bedside Grant (Collaborator: NIH)}
        {Jul 2010}{Present}
\item[]
\resemployer[End-to-end management solution for neuroimaging research project
        including subject tracking and medical charting, lab and assessment
        result management, billing, and auditing.]{Neuroimaging Research
        Database System}{Tulsa, OK}
    \resjob[Managing and supervising development. Specific personal
        responsibilities include documentation, project management, client
        interaction, and development of the auditing, report generation, and
        cost tracking/billing subsystems.]
        {IV Consulting (Client: Laureate Institute for Brain Research)}
        {Sep 2010}{Present}
\item[]
\resemployer[Web-based version of LPCH's legacy pen-and-paper intake system.
        Manages the creation of new patients and basic data collection.
        Generates patient reports for medical charts.]
        {Laureate Psychiatric Clinic and Hospital Electronic Intake System}
        {Tulsa, OK}
    \resjob[Supervised development of the entire system; responsible for
        development of report generation and clinical staff views for patient
        tracking. Managed documentation and client interactions.]
        {IV Consulting (Client: LPCH)}{Sep 2010}{Nov 2010}
\item[]
\resemployer[Network monitoring and visualization tool for the passive
        identification of network protocols using signatures.]{SAND/DVNE}
        {Tulsa, OK}
    \resjob[Led a network monitoring research group; designed and implemented
        a protocol identification library (SAND). Oversaw successful test
        deployment at FAA Computer Security Incident Response Center.
        Co-developed a multi-touch network traffic visualization tool (DVNE).
        Actively maintaining the library.]
        {Enterprise Security Group, University of Tulsa}{May 2007}{Present}
\item[]
\resemployer[Citizen-facing relief management system for disaster response;
        includes web service and IVR (phone) data collection and reporting
        capabilities. Senior semester capstone project from Senior Software
        course.]{Disastro}{Tulsa, OK}
    \resjob[Served as project lead and IVR developer. Responsibilities focused
        upon design, architecture, specification, documentation, developer
        coordination, and project management.]{Senior Software, University of
        Tulsa}{Jan 2009}{May 2009}
\item[]
\resemployer[Selected example class projects from University of Tulsa
        coursework.]{Sample Class Projects}{Tulsa, OK}
    \resjob[Pascal compiler front-end, Intrusion Detection System (Snort subset
        rule compatible), Web server, Comprehensive IT system deployment plan,
        Top-down corporate risk assessment (team), Formal model for IT
        contingency planning, Reinforcement learner agent for Infinite Mario]
        {University of Tulsa}{Aug 2005}{May 2011}
\end{itemize}

\resheading{Conferences}
\begin{itemize}
    \item[] \resconference{USENIX Security Symposium}{Participant (2009 - 2010)}
        \ressubconference{Workshop: Cyber Security Experimentation and Test}
        {Speaker (2010)}
        \ressubconference{Event: Poster Session}{Presenter (2009)}
    \item[] \resconference{Blackhat USA}{Participant (2010)}
    \item[] \resconference{DEFCON}
        {Human (2008, 2010), Speaker (2009)}
    \item[] \resconference{University of Tulsa Student Research Colloquium}
        {General Co-Chair (2010), Speaker and Session Chair (2009)}
        \ressubconference{Cyber Security and Critical Infrastructure Symposium}
        {Speaker and Symposium Chair (2010)}
    \item[] \resconference{International Conference on Internet Computing (ICOMP) at WORLDCOMP}
        {Speaker (2009)}
    \item[] \resconference{Computer Security and Information Intelligence Research
        Workshop (CSIIRW)}{Speaker (2009)}
    \item[] \resconference{International Conference for High Performance
        Computing, Networking, Storage and Analysis (SC)}{Participant (2008)}
    \item[] \resconference{IT Security World}{Exhibitor (2008)}
\end{itemize}

\footnotetext[1]{Denotes a peer-reviewed publication}
\resheading{Publications and Presentations}
\begin{itemize}
\item[] \resbib{``The Blunderdome: An Offensive Exercise for Building Network, Systems, and
    Web Security Awareness''\footnotemark[1]}{Paper at CSET 2010 at 19th USENIX Security
    Symposium, 2010. G Louthan, W Roberts, M Butler, and J Hale.}
\item[] \resbib{``Toward Sensitive Information Redaction in a Collaborative,
    Multilevel Security Environment''\footnotemark[1]}{Paper at WikiSym 2010,
    2010. P Gehres, N Singleton, G Louthan, and J Hale.}
\item[] \resbib{``Towards Formal Analysis of Cyber-Physical Systems''}
    {Presentation at the Cyber Security and
    Critical Infrastructure Symposium at the 2010 TU Student 
    Research Colloquium,
    2010. G Louthan, N Singleton, M Papa, and J Hale.}
\item[] \resbib{``Large-scale Multitouch Interactive Network Visualization''}{Poster at
	the 18th USENIX Security Symposium, 2009. C Pollet, 
	G Louthan and J Hale.}
\item[] \resbib{``SAND: An Architecture for Signature-based Automatic Network Protocol
    Detection''}{Poster at 18th USENIX Security Symposium, 2009.
    G Louthan and J Hale.}
\item[] \resbib{``Hack Like the Movie Stars: A Big-Screen Multitouch Network Monitor''}
    {Presentation at DEFCON 17, 2009. G Louthan, C Pollet, and J Hale.}
\item[] \resbib{``Toward Robust and Extensible Network Protocol
    Identification''\footnotemark[1]}{Paper at ICOMP '09, 2009. G Louthan, C McMillan,
    C Johnson, and J Hale.}
\item[] \resbib{``Content-based Alternatives to Conventional Network
    Monitoring''\footnotemark[1]}{Paper at CSIIRW '09, 2009. G Louthan,
    B Deetz, M Walker, and J Hale.}
\item[] \resbib{``Communication without Boundaries: Breaching the Great Firewall of
    China''}{Presentation at 2009 TU Student Research Symposium and
    Regional Meeting of AAAS-SWARM, 2009. G Louthan and J Hale.}
\end{itemize}

\resheading{Awards and Honors}
\begin{itemize}
    \setlength{\itemsep}{0mm}
    \item[] \resentry{General Co-Chair, TU Student Research Colloquium}{2010}
    \item[] \resentry{Chair, TU Student Research Colloquium Computer Security 
                    \newline
                    Special Topic Symposium}{2010}
    \item[] \resentry{Honorable Mention, Best Presentation at AAAS-SWARM}{2009}
    \item[] \resentry{Runner-Up, Donald W. Reynolds Governor's Cup \newline Business
                    Plan Competition}{2007}
    \item[] \resentry{University of Tulsa Presidential Scholar}{2005--09}
\end{itemize}
\end{document}
